---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

**INTRO: This is a package created as an assignment for STAT 547. It is still under development and may contain kinks. It will hopefully be useful, at least to me, to create anova plots. I often work with simple experimental studies with AxB designs and one of the most common ways to analyze the data is with anovas. However, I was surprised to find out that although there are packages that display the results of anova analysis, there isn't really an easy, automatic way to plot it. This package is an attempt to make the process easier and more intuitive for me.**

### anovaplot



### Installation

```{r installation, eval = FALSE}
devtools::install_github("rishadhabib/anovaplot")
```
  
### Quick demo

Binding two factors via `fbind()`:

```{r}
library(foofactors)
a <- factor(c("character", "hits", "your", "eyeballs"))
b <- factor(c("but", "integer", "where it", "counts"))
```

Simply catenating two factors leads to a result that most don't expect.

```{r}
c(a, b)
```

The `fbind()` function glues two factors together and returns factor.

```{r}
fbind(a, b)
```

Often we want a table of frequencies for the levels of a factor. The base `table()` function returns an object of class `table`, which can be inconvenient for downstream work. Processing with `as.data.frame()` can be helpful but it's a bit clunky.

```{r}
set.seed(1234)
x <- factor(sample(letters[1:5], size = 100, replace = TRUE))
table(x)
as.data.frame(table(x))
```

The `freq_out()` function returns a frequency table as a well-named `tbl_df`:

```{r}
freq_out(x)
```
